---
title: "Using plotRegulome"
author: "Mireia Ramos-Rodríguez"
output: 
  BiocStyle::html_document:
    toc: TRUE
    number_sections: TRUE
bibliography: library.bib
vignette: >
  %\VignetteIndexEntry{Using plotRegulome}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```


# Introduction

The `plotRegulome` package has been developed with the idea of helping users produce and modify the [Islet Regulome Browser](http://isletregulome.com/isletregulome/) plots.

# Quick start

```{r, eval=F}
library(plotRegulome)

## Download IRB database
# dir <- "~/data/"
# path <- downloadIRB(output_dir=dir) # Download IRB data, returns path for database

## Define parameters for plotting
coordinates <- "chr13:28354157-28550368"#"chr5:50678921-51318155"
snps_dataset <- "70KforT2D"
contacts_dataset <- "PDX1"
maps_dataset <- "chromatinClassesReduced"
cluster_dataset <- "enhancerClusters"
tfs_dataset <- "adult"
dir <- "~/data/IRB/"

## Call ploRegulome function
plotRegulome(coordinates=coordinates,
             snps_dataset=snps_dataset,
             contacts_dataset=contacts_dataset,
             maps_dataset=maps_dataset,
             cluster_dataset=cluster_dataset,
             tfs_dataset=tfs_dataset,
             path=dir)

```


# Datasets

In order to download all necessary datasets to plot islet data with this package, there is a wrapper function that does it for you. You just need to provide the path where the datasets for the IRB need to be stored.

```{r download-irb, eval=FALSE}
dir <- "~/data/"

downloadIRB(output_dir=dir) # Download IRB data
```

You will see that the donwloaded data has the following structure:

```
IRB_database
|-- code
|-- hg19
|   |-- clusters
|   |-- genes
|   |-- maps
|   |-- snps
|   |-- tfs
|   `-- virtual4c
|       |-- 1
|       |-- 2
|       |-- 3
|       |-- 4
|       |-- 5
|       |-- 6
|       |-- 7
|       |-- 8
|       `-- 9
`-- shared

```

Each folder inside `hg19` contains the datasets related to selectable data, summarized in the table below:

```{r echo=FALSE}
library(knitr)
library(kableExtra)

dat <- read.delim("table_datasets.csv")

kable(dat[,-1],
      caption="Selectable datasets for plotting.") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 10) %>%
  pack_rows("Clusters", 1, 5) %>%
  pack_rows("Maps", 6, 9) %>%
  pack_rows("SNPs", 10, 12) %>%
  pack_rows("TFs", 13, 15)
```

The name used for appropriatly calling datasets are listed in the column `Dataset` and in the documentation of `plotRegulome`. 

# Plotting

```{r}
plotRegulome(randomIRB=T,
             path=dir)
```


Please check `?plotRegulome` or the __Datasets__ section to see all available datasets and their code names.

```{r, width=12, height=10}
library(plotRegulome)

coordinates <- "chr13:28354157-28550368"#"chr5:50678921-51318155"
snps_dataset <- "70KforT2D"
contacts_dataset <- "PDX1"
maps_dataset <- "chromatinClassesReduced"
cluster_dataset <- "enhancerClusters"
tfs_dataset <- "adult"
path <- "~/data/IRB/"

plotRegulome(coordinates=coordinates,
             snps_dataset=snps_dataset,
             contacts_dataset=contacts_dataset,
             maps_dataset=maps_dataset,
             cluster_dataset=cluster_dataset,
             tfs_dataset=tfs_dataset,
             path=path)

```



# References
