---
title: "Using plotRegulome"
author: "Mireia Ramos-Rodríguez"
output: 
  BiocStyle::html_document:
    toc: TRUE
    number_sections: TRUE
bibliography: library.bib
vignette: >
  %\VignetteIndexEntry{Using plotRegulome}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = FALSE
)
```

```{r setup}
library(plotRegulome)
```

# Introduction


# Datasets

In order to download all necessary datasets to plot islet data with this package, there is a wrapper function that does it for you. You just need to provide the path where the datasets for the IRB need to be stored.

```{r download-irb, eval=FALSE}
downloadIRB(output_dir=".") # Download IRB data
```

You will see that the donwloaded data has the following structure:

```
IRB_database
|-- code
|-- hg19
|   |-- clusters
|   |-- genes
|   |-- maps
|   |-- snps
|   |-- tfs
|   `-- virtual4c
|       |-- 1
|       |-- 2
|       |-- 3
|       |-- 4
|       |-- 5
|       |-- 6
|       |-- 7
|       |-- 8
|       `-- 9
`-- shared

```

Each folder inside `hg19` contains the datasets related to the type of data.

```{r echo=FALSE}
dat <- read.delim("table_datasets.csv")

knitr::kable(dat)
```



# Plotting

```{r}
coordinates <- "chr5:50678921-51318155"
snps_dataset <- "70KforT2D"
contacts_dataset <- "ISL1"
maps_dataset <- "chromatinClassesReduced"
cluster_dataset <- "enhancerClusters"
tfs_dataset <- "adult"
path <- "~/data/IRB/"

plotRegulome(coordinates=coordinates,
             snps_dataset=snps_dataset,
             contacts_dataset=contacts_dataset,
             maps_dataset=maps_dataset,
             cluster_dataset=cluster_dataset,
             tfs_dataset=tfs_dataset,
             path=path)

```



# References
